Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-11-18 version3/version3.tex
updates

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tikz}

@@

%custom commands
\newcommand{\R}{\mathbf{R}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\num}{\text{num}}
\newcommand{\obs}{\text{obs}}
\newcommand{\D}{\mathfrak{D}}
\newcommand{\Ro}{\mathcal{R}_0}
\newcommand{\lap}{{\mathcal{L}}}
\renewcommand\vec{\mathbf}
\newcommand{\mat}[1]{\mathsf{#1}}
\newcommand{\U}{\mathcal{U}}

%insitute command
\usepackage{etoolbox}
\makeatletter
\providecommand{\institute}[1]{% add institute to \maketitle
	\apptocmd{\@author}{\end{tabular}
	\par
	\begin{tabular}[t]{c}
		\small \textit{#1}}{}{}
}
\makeatother

@@

	\subsection{Numerical discretization}
\section{Results}
	\subsection{Existence of solutions and basic reproduction numbers}

@@

>>>>

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{amsthm}

@@

%custom commands
\newcommand{\R}{\mathbf{R}}
\newcommand{\C}{\mathbf{C}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\num}{\text{num}}
\newcommand{\obs}{\text{obs}}
\newcommand{\D}{\mathfrak{D}}
\newcommand{\Ro}{\mathcal{R}_0}
\newcommand{\lap}{{\mathcal{L}}}
\renewcommand\vec{\mathbf}
\newcommand{\mat}[1]{\mathsf{#1}}
\newcommand{\U}{\mathcal{U}}

\newtheorem{theorem}{Theorem}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}

%intsitute command
\usepackage{etoolbox}
\makeatletter
\providecommand{\institute}[1]{% add institute to \maketitle
	\apptocmd{\@author}{\end{tabular}
	\par
	\begin{tabular}[t]{c}
		\small \textit{#1}}{}{}
}
\makeatother

@@

	\subsection{Numerical discretization}

\section{Results}
	\subsection{Existence of solutions and basic reproduction numbers}
		We define $\vec{x} = (S,  A, I, R)$ and $\vec{x}_0 = (S_0, A_0, I_0, R_0)$.
		\begin{theorem}
			Let $0 \leq \vec{x}_0 \leq N$ be the initial datum.
			Then there exists a unique in time solution $\vec{x}$ of the initial value problem (\ref{eq:model}) without diffusion over $C \subset U \subset \R^4 \times \R^1$ where $C$ is a compact set that contains $(\vec{x}_0, t_0)$.
			Moreover, the solution is $\C^1$.
		\end{theorem}
		\begin{proof}
			Since $\vec{x}_t = f(\vec{x},t)$ is $\C^1$ on the open set $U \subset \R^4 \times \R^1$, it follows that there exists a solution of (\ref{eq:model}) without diffusion through the point $\vec{x}_0$ at $t = t_0$ for $|t - t_0|$ sufficiently small.
			Moreover, $\vec{x} (t, t_0,\vec{x_0})$ is a $\C^1$ function \cite{dynamics}.
			Since $C$ is a compact set containing $(\vec{x}_0, t_0)$, then the solution $\vec{x} (t, t_0, \vec{x}_0)$ can be uniquely extended backward and forward in $t$ up to the boundary of $C$ \cite{dynamics}.
		\end{proof}

		\begin{conjecture}
			Let $0 \leq \vec{x}_0 \leq N$ the initial datum.
			Then there exists a unique global in time solution $\vec{x}$ of the initial boundary value problem (\ref{eq:model}).
		\end{conjecture}

		An important parameter in understanding the initial growth of the disease is the basic reproduction number.
		\begin{definition}[Basic Reproduction Number]
			The basic reproduction number $\Ro$ can be computed using the next generation of the model without diffusion.
			Since the infected individuals are in $A$ and $I$, new infections ($\mathcal{F}$) and transitions between compartments ($\mathcal{V}$) can be rewritten as
			\begin{align*}
				\mathcal{F} &= \begin{pmatrix} \omega (\beta_A A + \beta_I I) \frac{S}{N} \\ 0 \end{pmatrix}, &
				\mathcal{V} &= \begin{pmatrix} (\gamma_A + \delta) A \\ \gamma_I - \delta A \end{pmatrix}.
			\end{align*}
			Thus, $\Ro = \rho (\mat{F} \mat{V}^{-1})$ of the next generation matrix
			\begin{equation*}
				\mat{F} \mat{V}^{-1} = \begin{pmatrix} 
				\frac{S_0 \omega_0 \beta_A}{N (\gamma_A + \delta)} + \frac{S_0 \omega_0 \beta_I \delta}{N \gamma_I (\gamma_A + \delta)} & 
				\frac{S_0 \omega_0 \beta_I}{N \gamma_I} \\ 
				0 & 0 \end{pmatrix}.
			\end{equation*}
			So,
			\begin{equation} \label{eq:ro}
				\Ro =  \frac{\omega_0}{\gamma_A + \delta}  \left( \beta_A + \beta_I \frac{\delta}{\gamma_I} \right) \frac{S_0}{N}.
			\end{equation}
		\end{definition}
		This number is dimensionless and has an epidemiological meaning.
		The first term represents the transmission rate by asymptomatic individuals, and the second term represents the transmission rate by symptomatic individuals.

@@

\section*{Appendix}
	\subsection*{Nomenclature (Units are indicated in brackets.)}
		\begin{table}[h!]
			\begin{tabular}{c c}
				\textbf{Latin symbols} & \\
				$A$ & Asymptomatic infected individuals [individuals] \\
				$I$ & Symptomatic infected individuals [individuals] \\
				$N$ & Total population of individuals [individuals] \\
				$R$ & Removed individuals [individuals] \\
				$S$ & Susceptible individuals [individuals] \\
				\textbf{Greek symbols} & \\
				$\beta_j$ & Contact rate of compartment $j$ [days\textsuperscript{-1}] \\
				$\gamma_j$ & Recovery rate of compartment $j$ [days\textsuperscript{-1}] \\
				$\delta$ & Rate of asymptomatic individuals that may develop symptoms [days\textsuperscript{-1}]
			\end{tabular}
		\end{table}
